---
title: "UPDATE Project Template"
author: "UPDATE Name"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

data.rankings = data.frame(
  "City" = c(
    "Austin TX",
    "Baltimore MD",
    "Boston MA",
    "Charlotte NC",
    "Chicago IL",
    "Cleveland OH",
    "Columbus OH",
    "Dallas TX",
    "Denver CO",
    "Detroit MI",
    "El Paso TX",
    "Houston TX",
    "Indianapolis IN",
    "Kansas City MO",
    "Las Vegas NV",
    "Long Beach CA",
    "Los Angeles CA",
    "Louisville KY",
    "Memphis TN",
    "Milwaukee WI",
    "Minneapolis MN",
    "Nashville TN",
    "New York City NY",
    "Oakland CA",
    "Oklahoma City OK",
    "Philadelphia PA",
    "Phoenix AZ",
    "Portland OR",
    "San Antonio TX",
    "San Diego CA",
    "San Francisco CA",
    "San Jose CA",
    "Seattle WA",
    "Tucson AZ",
    "Washington DC"
  )
)

# Default all cities to 30
data.rankings$firearm.deaths = 30  

# Assign custom values
data.rankings$firearm.deaths[data.rankings$City == "Indianapolis IN"] <- 2
data.rankings$firearm.deaths[data.rankings$City == "Philadelphia PA"] <- 3
data.rankings$firearm.deaths[data.rankings$City == "Louisville KY"]   <- 4
data.rankings$firearm.deaths[data.rankings$City == "Tucson AZ"]       <- 6
data.rankings$firearm.deaths[data.rankings$City == "Houston TX"]      <- 1
data.rankings$firearm.deaths[data.rankings$City == "Chicago IL"]      <- 5

# Assign 10s
ten_cities <- c("Memphis TN", "Detroit MI", "Cleveland OH", 
                "Milwaukee WI", "Baltimore MD", "Kansas City MO")
data.rankings$firearm.deaths[data.rankings$City %in% ten_cities] <- 10

# Assign Washington DC = 0
data.rankings$firearm.deaths[data.rankings$City == "Washington DC"] <- 0
```

## Data
Provide a brief paragraph (3-4 sentences) on the data used in this project. This includes the specific source(s), the size, and the specific temporal and spatial constraints.

## Analysis

### City 1: xxx
Provide justification of similarity for each city (4-5 sentences each) 
Each justification should include at least four specific reasons for similarity
Each reason should include a relevant statistical reference

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create a vector of random numbers 1–34
random_values <- sample(1:34, size = nrow(data.rankings) - 1, replace = FALSE)

# Assign fake.data
data.rankings$fake.data <- NA
data.rankings$fake.data[data.rankings$City == "Washington DC"] <- 0
data.rankings$fake.data[data.rankings$City != "Washington DC"] <- random_values

#### 
# Add a highlight column
data.rankings$Highlight <- ifelse(data.rankings$City == "Washington DC", "DC",
                                  ifelse(data.rankings$City == "Chicago IL", "Chicago", "Other"))

ggplot(data.rankings, aes(x = firearm.deaths, y = fake.data, label = City, color = Highlight)) +
  geom_point(size = 3) +
  geom_text(vjust = -0.5, size = 3) +
  scale_color_manual(values = c("DC" = "green", "Chicago" = "red", "Other" = "steelblue")) +
  labs(
    title = "Scatterplot of Firearm Deaths vs Fake Data",
    x = "Firearm Deaths",
    y = "Fake Data",
    color = "City"
  ) +
  theme_minimal()
```

### City 2: xxx


